Google - Isolated Sign Language Recognition

### 2023-03-02 cvpr_final_report/PaperForReview.tex
Add expected result

We will use the raw data extraced from MediaPipe Holistic Solution which record every movement in video by landmark.
Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.

@@

MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
The way that MediaPipe Holistic Solution record every movement of human face, body and hands is landmarks.
Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
These dots help a computer to understand where these important areas are and how they are moving.

%------------------------------------------------------------------------
\section{Expected Result}

>>>>

We will use the raw data extracted from MediaPipe Holistic Solution which record every movement in video by landmark.
Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.

@@

MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
These dots help a computer to understand where these important areas are and how they are moving.

%------------------------------------------------------------------------
\subsection{Model}

%------------------------------------------------------------------------
\section{Expected Result}
We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.
